% CREATED BY DAVID FRISK, 2016
% MODIFIED BY ALEXANDER HÅKANSSON, 2017
\large
\begin{flushleft}
\textbf{\varthetitle}\\
\varthesubtitle\\[0.7cm]
\end{flushleft}
JESPER JAXING\\
ALEXANDER HÅKANSSON\\
MAXIM GORETSKYY\\
GMAL TCHAEFA\\
AXEL OLIVECRONA\\
JONATAN ALMÉN\\
\normalsize
\textit{Department of Computer Science and Engineering\\
Chalmers University of Technology\\
University of Gothenburg}\\[0.7cm]
Bachelor of Science Thesis
\setlength{\parskip}{0.5cm}

\thispagestyle{plain}			% Supress header 
\setlength{\parskip}{0pt plus 1.0pt}
\section*{Abstract}
Artificial neural networks have in recent years found success in a variety of fields and in this thesis we evaluate if they can be used in place of classic recommender systems. A recurrent neural network was built to automatically recommend users of social platforms content that they would find interesting, in this thesis the website Reddit was used as a the source for training, testing and validation data. Reddit was chosen because of availability of data and that it was naturally labelled. Several baselines were under consideration such as n-gram based models and a text classification library developed at Facebook. We were able to surpass our baselines and will discuss possible extensions and feature work.

\section*{Sammanfattning}
Artificiella neurala nätverk har på de senaste åren haft stor framgång i många olika områden. I denna tes utvärderar vi om artificiella neurala nätverk kan fylla platsen som i dagsläget okuperas av mer klassiska rekommendationssystem. Ett rekurrent neuralt nätverk byggdes för att automatiskt kunna rekommendera användare på sociala platformar innehåll som intresserar dom. Den platform som vi använde som källa för tränings-, testning- och valideringsdata var Reddit. Reddit valdes främst för att data var naturligt märkt och för att datan var tillgänglig. Flera olika baslinjer användes så som n-gram baserade modeller och ett text klassificerings bibliotek utvecklat av Facebook. Vi lyckades att slå våra baslinjer och diskuterar även möjliga påbyggnader.

% KEYWORDS (MAXIMUM 10 WORDS)
\vfill
\textbf{Keywords:} Artifial Neural Networks, ANN, Recurrent Neural Networks, RNN, Recommender System, Reddit, Automatic recommendation, Text classification.

\newpage				% Create empty back of side
\thispagestyle{empty}
\mbox{}